### 2024-04-20 docs/SOSP 2024/motivation.tex
Minor edit

Consider a model with four trees, two 
trees of depth 1 and two of depth 2 (\circled{A} in Figure \ref{Fig:HIRExample}).
% We use this model as our running example throughout this section.
We first describe the simple schedule shown in Figure \ref{fig:schedulea} that processes one tree at a time 
for all input rows\footnote{Since the scheduling constructs are fairly intuitive, we 
defer a detailed explanation of the scheduling language to Section~\ref{sec:schedule}.}.
In this schedule, the loop over the trees is split into two -- one that
iterates over the first two trees (Trees 1 and 2 with depth 1) and 
the second that iterates over the last two trees (Trees 3 and 4 with
depth 2). Straightforward traversal of trees requires a \op{while} loop
and involves branching to check if a leaf has been reached. 
One way to avoid this, as done in this schedule, is to unroll the 
tree walks for each tree. 
When the schedule specifies that the tree walks should be unrolled, 
\Treebeard{} pads the trees so that all leaves of a tree are at the same depth
(\circled{B} in Figure~\ref{Fig:HIRExample}). 
The concrete implementation of this schedule (in \Treebeard{}'s IR) 
is as shown in Figure \ref{fig:schedulea}\footnote{We do not show 
the full MLIR listing of the IR. Instead, we present inference routines 
as pseudo-code for the sake of clarity.}.
This schedule is ideally suited for a single-core CPU. It maximizes 
the reuse of trees in the L1 cache. However, it doesn't exploit  
any parallelism.

>>>>

Consider a model with four trees, two 
trees of depth 1 and two of depth 2 (\circled{A} in Figure \ref{Fig:HIRExample}).
% We use this model as our running example throughout this section.
We first describe the simple schedule shown in Figure \ref{fig:schedulea} that processes one tree at a time 
for all input rows\footnote{Since the scheduling constructs are fairly intuitive, we 
defer a detailed explanation of the scheduling language to Section~\ref{sec:schedule}.}.
In this schedule, the loop over the trees is split into two -- one that
iterates over the first two trees (Trees 1 and 2 with depth 1) and 
the second that iterates over the last two trees (Trees 3 and 4 with
depth 2). Straightforward traversal of trees requires a \op{while} loop
and involves branching to check if a leaf has been reached. 
One way to avoid this, as done in this schedule, is to unroll the 
tree walks for each tree. 
When the schedule specifies that the tree walks should be unrolled, 
\Treebeard{} pads the trees so that all leaves of a tree are at the same depth
(\circled{B} in Figure~\ref{Fig:HIRExample}). 
The concrete implementation of this schedule (in \Treebeard{}'s IR) 
is as shown in Figure \ref{fig:schedulea}\footnote{We do not show 
the full listing of the IR. Instead, we present inference routines 
as pseudo-code for the sake of clarity.}.
This schedule is ideally suited for a single-core CPU. It maximizes 
the reuse of trees in the L1 cache. However, it doesn't exploit  
any parallelism.
